% !TEX encoding = UTF-8 Unicode
\documentclass[a4paper]{article}

\usepackage[
    top=0.79in,
    bottom=0.79in,
    left=0.79in,
    right=0.79in,
]{geometry}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{10pt}
\newlength{\tablewidth}

\setlist[itemize]{topsep=0em, itemsep=0.0em}
\setlist[itemize,1]{before=\vspace{-1em}}

\newenvironment{period}[2]{%
\newcommand{\sarma}{#2}%
\setlength{\tablewidth}{\linewidth}
\addtolength{\tablewidth}{-2\tabcolsep}
\begin{tabular}{@{}p{0.75\tablewidth}>{\raggedleft\arraybackslash}p{0.25\tablewidth}@{}}%
#1 \newline
\begin{itemize}
}{%
\end{itemize} & \sarma \\%
\end{tabular}\\
}

\newenvironment{period_empty}[2]{%
\newcommand{\sarma}{#2}%
\setlength{\tablewidth}{\linewidth}
\addtolength{\tablewidth}{-2\tabcolsep}
\begin{tabular}{@{}p{0.75\tablewidth}>{\raggedleft\arraybackslash}p{0.25\tablewidth}@{}}%
#1
}{& \sarma \end{tabular}}

\newenvironment{skills}{%
\setlength{\tablewidth}{\linewidth}
\addtolength{\tablewidth}{-2\tabcolsep}
\begin{tabular}{@{}p{0.15\tablewidth}p{0.85\tablewidth}@{}}
}{%
\end{tabular}
}

\titleformat{\section}{\uppercase}{}{0pt}{}[{\vspace{0.5em}\titlerule}]
\titleformat{\subsection}{\bf}{}{0pt}{}{}
\titlespacing{\section}{0pt}{1em}{0.5em}
\titlespacing{\subsection}{0pt}{0pt}{0.1em}

\begin{document}
\fontfamily{\sfdefault}
\selectfont

\begin{minipage}{.5\textwidth}
\LARGE{Marin Koštić}\\
\normalsize{Slavka Kolara 45b, Velika Gorica, Croatia}
\end{minipage}%
\begin{minipage}{.5\textwidth}
\raggedleft
\href{mailto:kosticmarin@gmail.com}{kosticmarin@gmail.com}\\
+385 91 931 9327 \\
\href{https://github.com/kosticmarin}{github.com/kosticmarin}\\
\href{https://www.linkedin.com/in/marin-koštić-495949155}{linkedin/kosticmarin}
\end{minipage}

\vspace{1em}


\section{education}
\subsection{University of Zagreb, Faculty of Electrical Engineering and Computing \hspace*{\fill}Croatia}
\begin{period_empty}{Master of Computer Science}{2016--2018} 
\end{period_empty}
\begin{period_empty}{Bachelor of Computer Engineering}{2012--2016}
\end{period_empty}

\section{master thesis}
\textbf{Title}: Local methods for Color Image Enhancement\\
\textbf{Supervisor}: Prof. Dr. Sc. Sven Lončarić\\
\textbf{Description}: This thesis explored research in the field of digital image enhancement, more specifically on the subject of local methods for color image enhancement.

\section{bachelor thesis}
\textbf{Title}: Embedded system for Temperature and Humidity measurement\\
\textbf{Supervisor}: Prof. Dr. Sc. Hrvoje Mlinarić\\
\textbf{Description}: Designing an embedded system based on ESP8266 processor that is connected
to temperature and humidity sensor via I2C bus.


\section{experience}
\subsection{Amodo \hspace*{\fill}Zagreb}
\begin{period}{Data Engineer}{Sep. 2018 -- Present}
    \item Developing Amodo telematics Usage-based insurance platform in a small team of engineers.
    (Django, PostgreSQL)
    \item Developing scoring systems based on milage from GPS data recorded by smartphone SDK
    and user behaviour based on smartphone usage. Integrating data enrichment and contextualization
    pipelines based on GPS data using OSM, Google and HERE maps. (Java, Kafka, Cassandra)
    \item Research and Development of sensor fusion from smartphone sensors to detect user Transportation
    mode and behavioural events in traffic using Machine Learning. (Python, Tensorflow) 
     
\end{period}


\begin{period}{DevOps Engineer, Student}{Jul. 2017 -- Sep. 2018}
    \item Maintaining server infrastructure as code on AWS and Digital Ocean. (Ansible)
\end{period}


\subsection{Faculty of Electrical Engineering and Computing \hspace*{\fill}Zagreb}
\begin{period}{Teaching assistant}{Jan. 2015 -- May. 2015}
    \item Demonstrator at Laboratory exercises in \textit{Computer Architecture 1} class
\end{period}


\section{skills}
\textbf{Programming Languages}:\\
Advanced: Python, Java\\
Intermediate: Rust\\
Basic: C/C++\\

\textbf{Miscellaneous}:\\
Advanced: PostgreSQL\\
Intermediate: Git, Ansible, Linux/Unix, SQL, PostGIS, Cassandra, Kafka, Django, Tensorflow, TDD\\
Basic: OpenCV, Mediapipe, Docker, Kubernates, Bazel\\


\section{Languages}
\textbf{Croatian}: Mother tongue\\
\textbf{English}: Professional working proficiency \hspace*{\fill} Cambridge CEA: C1


\section{interests}
Outside of work I like to spend my time training which includes Brazilian Jiu Jitsu and Cycling.

\end{document}
